Soling at the 2000 Summer Olympics

### 2020-07-27 inst/f1points.Rmd
use formula1_points_system() instead

```{r,echo=FALSE,print=FALSE}
top <- 11
points_inaugural <- c(8,6,4,3,2)
```

@@

```{r, label=calcpoints, echo=FALSE, cache=TRUE}
p <- c(25, 18, 15, 12, 10, 8, 6, 4, 2, 1, 0, 0)
points_real <- p
points_inaugural <- c(8,6,4,3,2)
dp2016 <- ordertable2points(as.ordertable(F1_table_2016[seq_len(top),]),p)
dp2016 <- sort(dp2016,decreasing=TRUE)
dp2016[] <- seq_along(dp2016)
m2016 <- maxp(H2016)
m2016 <- sort(m2016,decreasing=TRUE)
m2016[] <- seq_along(m2016)

>>>>

```{r,echo=FALSE,print=FALSE}
top <- 11
```

@@

```{r, label=calcpoints, echo=FALSE, cache=TRUE}
p <- formula1_points_systems()[[1]]
dp2016 <- ordertable2points(as.ordertable(F1_table_2016[seq_len(top),]),p)
dp2016 <- sort(dp2016,decreasing=TRUE)
dp2016[] <- seq_along(dp2016)
m2016 <- maxp(H2016)
m2016 <- sort(m2016,decreasing=TRUE)
m2016[] <- seq_along(m2016)
